---
title: "RW_zebrafinch_Burley"
author: "ML"
date: "23/12/2019"
output: html_document
output:
  html_document:
    code_download: true
    code_folding: hide
    depth: 4
    number_sections: no
    theme:  cosmo # “default”, “cerulean”, “journal”, “flatly”, “darkly”, “readable”, “spacelab”, “united”, “cosmo”, “lumen”, “paper”, “sandstone”, “simplex”, “yeti”
    toc: yes
    toc_float: yes
    toc_depth: 4
  pdf_document:
    toc: yes
subtitle: Electronic Supplementary Material - literature survey
#bibliography: references.bib
#biblio-style: "apalike"
#csl: nature.csl
link-citations: yes
---

## Setup
Knitter settings, loading packages and custom functions.   

```{r setup, eval = TRUE}
#kniter seetting
knitr::opts_chunk$set(
message = FALSE,
warning = FALSE, # no warnings
cache = TRUE,# Cacheing to save time when kniting
tidy = TRUE, 
echo = TRUE
#fig.width = 9
)

# cleaning up
rm(list=ls())

#load packages
pacman::p_load(tidyverse, # tidy family and related pacakges below
               readxl, #read Excel files
               bibliometrix, #bibliometric analyses
               kableExtra, # add features to a kable() output 
               ggplot2,
               ggrepel,
               #gridExtra, # may not use this
               purrr,    #functional programming tools
               magrittr, # extending piping
               pander,   # nice tables
               #ggbeeswarm, # making bee-swarm plots possible
               plotly,     # interactive plots using ggplot2
               png,         # reading png files
               revtools, #syste rev tools
               #grid,        # graphic layout manipulation
               formatR # provides a function tidy_source() to format R source automatically
               #nVennR, # Venn diagrams https://cran.r-project.org/web/packages/nVennR/vignettes/nVennR.html
               #rsvg, #displaying svg plots from nVennR
               #grImport2 #displaying svg plots from nVennR
)
```

## Aims   
To visualise the impact of publications Burley 1981 and Burley 1982 on academic literature:   
 1. showing highly cited papers and papers in high IF journals that cite works by Burley
 2. among these, which ones ae follow-up studies on the effects of colored bands on preference or reproduction in birds

### Literature (initial data set)    
We downloaded full bibliographic records of 201 papers citing Burley 1981 and 233 citing Burley 1982 from Scopus platform (as on 2019/12/22). The records were automatically deduplcated on Scopus platform, resulting in 401 unique records (including records for Burley 1981 and Burley 1982). The equivalent numbers were 201, 260 and 386 (unique) records when we used Web of Knowledge platform. We decided to use Scopus records, due to the higher total number of unique citing papers.   

#### Upload initial Scopus data set   
The records are stored in zebrafinch_Scopus.bib file - first we use bibliometrix and revtools function to load these into a data frame. Then, merge this data frame with the journal citation records.  

```{r load data, eval = TRUE}
### 1 Load bib file with records from Scopus (2019/12/23) into bibliometrix package to create data frame for anlayses:
tmp <- readFiles("./data/zebrafinch_Scopus.bib")
# Convert to a bibliometric data frame
bib <- convert2df(tmp, dbsource = "scopus", format = "bib")
rm(tmp)
#str(bib)
#dim(bib) #402 - ok
#length(unique(bib$TI)) #401
#which(bib$TI == bib$TI[duplicated(bib$TI)]) #rows 101 and 105 are duplicated
#rownames(bib[c(101, 105),]) #same paper, different formatting, remove one with rownames=="TTH A, 2010, ARCH TIERZ"
bib$longID <- rownames(bib) #add column with long paper ID made from rownames
bib <- bib %>% filter(longID != "TTH A, 2010, ARCH TIER") #remove one of the duplicates
#fix wrong journal name for Burley 1981
bib %>% filter(TI != "TTH A, 2010, ARCH TIER") #remove one of the duplicates
#paper by Burley 1981 has wrong journal (SO):bib %>% filter(bib$AU %in% grep("BURLEY", bib$AU, value=TRUE) & PY==1981) #Burley 1981 record - wrong journal (SO)
bib <- bib %>% mutate(SO=replace(SO, TI=="SEX RATIO MANIPULATION AND SELECTION FOR ATTRACTIVENESS", "SCIENCE")) 
bib <- bib %>% mutate(longID=replace(longID, TI=="SEX RATIO MANIPULATION AND SELECTION FOR ATTRACTIVENESS", "BURLEY N, 1981, SCIENCE")) 

### 2. Load same bib file into revtools creating differentky formatted dat frame (will be used for manual screening/labeling):
revdata <- read_bibliography("./data/zebrafinch_Scopus.bib")
#names(revdata)
#revdatanew$label
#length(unique(revdata$title)) #401
#which(duplicated(revdata$title)) #row 105
which(revdata$title == revdata$title[duplicated(revdata$title)]) #rows 101 and 105
#revdata[c(101, 105),] # same paper, different formatting, remove one with label==Tth2010328.1
revdata <- revdata %>% filter(label != "Tth2010328.1") #remove one of the duplicates
revdata$title <- gsub("  ", " ", revdata$title) #remove double space from one of the titles
revdata %>% filter(revdata$author %in% grep("Burley", revdata$author, value=TRUE) & year==1981) #Burley 1981 record - wrong journal (SO)
revdata <- revdata %>% mutate(journal=replace(journal, title=="Sex ratio manipulation and selection for attractiveness", "Science")) 

#compare data frame created in revtools with data frame created in bibliometrix
#length(intersect(tolower(revdata$title), tolower(bib$TI))) #401 - all matching titles (at lower case)
#setdiff(tolower(revdata$title), tolower(bib$TI)) #0 mismatches
#setdiff(tolower(bib$TI), tolower(revdata$title)) #0 mismatches

#write.csv(revdata, "Scopus_bib_as_df.csv", row.names = FALSE) #sve as Rdat, as csv messes up rows!
```

#### incorporate journals IF   
Adding data with Journal Impact Factors (InCite Journal Citation Reports:  Selected JCR Year: 2018 Selected Editions: SCIE,SSCI Selected Category Scheme: WoS).   

```{r journals, eval = TRUE}
#load journal data
journals_data <- read_excel("./data/JournalHomeGrid.xlsx", na = "NA", skip = 2, col_types = c("numeric", "text", "numeric", "skip", "numeric", "numeric")) %>% mutate_if(is.character, as.factor)
#names(journals_data)
#remove unnecessary columns and rename the other
#journals_data <- journals_data  %>% select(-"...4")
journals_data <- journals_data  %>% rename(Journal_Name = "Full Journal Title", 
                       Total_Cites = "Total Cites",
                       JIF = "Journal Impact Factor",
                       Eigenfactor_Score = "Eigenfactor Score"
                       )
journals_data <- mutate(journals_data, Journal_Name_lower = tolower(Journal_Name))
#check journal names
journals <- bib$SO #402
journals_list <- unique(tolower(journals)) #130
#intersect(journals_list, journals_data$Journal_Name_lower) #85
#setdiff(journals_list, journals_data$Journal_Name_lower) #45 unmatched, many books
#fix journal names (Scopus = JCR):
journals_data$Journal_Name_lower[grepl("ethology", journals_data$Journal_Name_lower)]
journals_data$Journal_Name_lower <- gsub("proceedings of the royal society b-biological sciences", "proceedings of the royal society b: biological sciences", journals_data$Journal_Name_lower, ignore.case = TRUE)
journals_data$Journal_Name_lower <- gsub("philosophical transactions of the royal society b-biological sciences", "philosophical transactions of the royal society b: biological sciences", journals_data$Journal_Name_lower, ignore.case = TRUE)
journals_data$Journal_Name_lower <- gsub("trends in ecology & evolution", "trends in ecology & evolution"
, journals_data$Journal_Name_lower, ignore.case = TRUE)
journals_data$Journal_Name_lower <- gsub("annual review of ecology evolution and systematics", "annual review of ecology and systematics", journals_data$Journal_Name_lower, ignore.case = TRUE)
journals_data$Journal_Name_lower <- gsub("ethology ecology & evolution", "ethology ecology and evolution", journals_data$Journal_Name_lower, ignore.case = TRUE)
journals_data$Journal_Name_lower <- gsub("emu-austral ornithology", "emu", journals_data$Journal_Name_lower, ignore.case = TRUE)

#marge journal info into bib2 dataframe
bib2 <- mutate(bib, Journal_Name_lower = tolower(SO))
bib2 <- left_join(bib2, journals_data, by = "Journal_Name_lower")
#str(bib2)
#dim(bib2) #437 - note some records were joined incorrectly (some duplicated data rows)!
bib2 <- distinct(bib2, .keep_all = TRUE)
#dim(bib2) #402
bib2 <- bib2 %>% filter(longID != "TTH A, 2010, ARCH TIER") #remove one of the duplicates
#write.csv(bib2, "./data/Scopus_bib_as_df.csv", row.names = FALSE)
rm(journals_data) #clean up
```

#### Data clean-up: author names   

Note: Burley appears both as "BURLEY N" and "BURLEY NT"! (similar issue for some other outhors)   
```{r authors, eval = TRUE}
#check author names as strings
authors <- bib2$AU #402 

#extract individual authors of citing papers into a vector of names
authors2 <- unlist(strsplit(authors, ";")) #these are authors in the reference lists!
authors2 <- unique(authors2[order(authors2)])
#View(test2) #see which names need cleaning
#write.csv(authors2, "./data/author_list_uncleaned.csv", row.names = FALSE)

#grep("BURLEY", authors2, value=TRUE) #3 forms - needs fixing

# We can do some cleaning where we suspect a mistake (especially author initials)
corrected <- paste(bib2$AU, ";", sep="")
corrected <- gsub("BURLEY N;", "BURLEY NT;", corrected, ignore.case = TRUE)
corrected <- gsub("BURLEY DN;", "BURLEY NT;", corrected, ignore.case = TRUE)
corrected <- gsub("CASPERS B;", "CASPERS BA;", corrected, ignore.case = TRUE)
corrected <- gsub("CLUTTONBROCK TH;", "CLUTTON BROCK TH;", corrected, ignore.case = TRUE)
corrected <- gsub("CUTHILL I;", "CUTHILL IC;", corrected, ignore.case = TRUE)
corrected <- gsub("CICHO M;", "CICHON M;", corrected, ignore.case = TRUE)
corrected <- gsub("TINBERGEN J;", "TINBERGEN JM;", corrected, ignore.case = TRUE)
bib2$AU <- corrected #add corrections

#save as a data frame
#write.csv(bib2, "Scopus_bib_as_df.csv", row.names = FALSE) #sve as Rdat, as csv messes up rows!
```

**Extended Data Table 1:**   
List of 401 bibliographic records used in the analyses (including Burley 1981 and Burley 1982).    

```{r scrollable table of 402 papers, include = FALSE, eval = FALSE}
bib2 %>% select(AU, PY, TI, SO, VL, PP, DT) %>% kable("html") %>%
    kable_styling("striped", position = "left") %>%
  scroll_box(width = "100%", height = "300px")
```


#### Coding contents of papers using Revtools    
Revtools has a screening tool which can be also used for adding lebels to records.   
Manually screened records to mark these on birds and coloured ring preference/reproductionas (labelled as "included", with additional marks for zebrafinch "ZF" and other birds "OB").     

```{r screen and label in revtools, eval = FALSE}
scr_tit_res <- screen_titles(revdata) # run revtools app with titles only
names(scr_tit_res)
table(scr_tit_res$screened_titles) #62 not excluded
scr_abs <- scr_tit_res %>% filter(screened_titles != "excluded") #filter out 62 abstracts that are not excluded for further screening
scr_abs_res <- screen_abstracts(scr_abs) # run revtools app with abstracts
names(scr_abs_res)
table(scr_abs_res$screened_abstracts) #32 selected
scr_abs_lab <- scr_abs_res %>% filter(screened_abstracts != "excluded") #filter out 32 abstracts that are not excluded for manual labeling
names(scr_abs_lab)
dim(scr_abs_lab)
scr_abs_lab %>% grepl("zebrafinch", title)
scr_abs_lab2 <- revdata %>% filter(revdata$title %in% scr_abs_lab$title) #  RE-FILTER THESE RECORDS FROM THE ORIGINAL DATASEST (REVTOOLS DOES NOT WONT TO RUN AGAIN OTHERWISE)
dim(scr_abs_lab2)
scr_abs_lab_res <- screen_abstracts(scr_abs_lab2) # run revtools app with abstracts again to add labels (ZF, OB)
dim(scr_abs_lab_res) #also saved to a file SCR_ABS_LAB_RES.csv
```

```{r add screening labels from revtools, eval = TRUE}
scr_abs_lab_res <- read.csv("./data/SCR_ABS_LAB_RES.csv")
#names(scr_abs_lab_res)
#table(scr_abs_lab_res$notes) #OB 10, ZF 22
bib2 <- bib2 %>% mutate(ring = ifelse(tolower(bib2$TI) %in% tolower(scr_abs_lab_res$title), "yes", "no")) 
#table(bib2$ring)
```


#### Initial plots   

See: http://r-statistics.co/Complete-Ggplot2-Tutorial-Part2-Customizing-Theme-With-R-Code.html#Annotation    

```{r initial plot by year and IF, eval = FALSE}
#scale points by TC (total citations)
table(is.na(bib2$JIF)) #46 missing - probably for book chapters etc. - remove?
  
ggplot(bib2, aes(x = PY, y = JIF, size = TC, alpha = 0.1)) + 
  geom_point(col = "grey") + 
  theme_minimal() +
  theme(legend.position="top") + 
  guides(colour = FALSE, alpha = FALSE) + guides(size=guide_legend("Total Citations")) + 
  labs(title="Impact", x="Publication Year", y="Journal Impact Factor", caption="Source: Scopus")
```

```{r plot by year and TC, eval = FALSE}
#scale points by JIF (Journal Impact Facto)
ggplot(bib2, aes(x=PY, y=TC, size=JIF, alpha=0.1)) + 
  geom_point(col = "grey") +
  theme_minimal() +
  theme(legend.position="top") + 
  guides(colour = FALSE, alpha = FALSE) + guides(size=guide_legend("Journal Impact Factor")) + 
  labs(title="Impact", x="Publication Year", y="Total Citations", caption="Source: Scopus")
```

With original and follow-up birs ring preference studies in blue:

```{r plot by year and IF ring, eval = FALSE}
#table(is.na(bib2$JIF)) #46 missing - probably for book chapters etc. - remove?
#scale points by TC (total citations)
ggplot(bib2, aes(x = PY, y = JIF, size = TC, alpha = 0.1)) + 
  geom_point(aes(col=ring)) + 
  theme_minimal() +
  theme(legend.position="top") + 
  guides(colour = FALSE, alpha = FALSE) + guides(size=guide_legend("Total Citations")) + 
  labs(title="Impact", x="Publication Year", y="Journal Impact Factor", caption="Source: Scopus")
```

```{r plot by year and TC ring, eval = TRUE}
#scale points by JIF (Journal Impact Facto)
ggplot(bib2, aes(x=PY, y=TC, size=JIF, alpha=0.1)) + 
  geom_point(aes(col=ring)) +
  theme_minimal() +
  theme(legend.position="top") + 
  guides(colour = FALSE, alpha = FALSE) + guides(size=guide_legend("Journal Impact Factor")) + 
  labs(title="Impact", x="Publication Year", y="Total Citations", caption="Source: Scopus")
```

With original and follow-up birds ring preference studies in blue and labels:

```{r plot by year and IF ring labels, eval = FALSE}
# Scale points by TC (total citations)

# table(is.na(bib2$JIF)) #46 missing - probably for book chapters etc. - remove:
bib3 <- bib2 %>% filter(!is.na(bib2$JIF))

# Filter required rows
bib3_sub1 <- bib3 %>% filter(ring == "yes" | JIF > 20, )

# Basic plot
gg <- ggplot(bib3, aes(x = PY, y = JIF, size = TC, alpha = 0.1)) + 
  geom_point(aes(col=ring)) + 
  theme_minimal() +
  theme(legend.position="top") + 
  guides(colour = FALSE, alpha = FALSE) + guides(size=guide_legend("Total Citations")) + 
  labs(title="Impact", x="Publication Year", y="Journal Impact Factor", caption="Source: Scopus")

# # Plot text and label ------------------------------------------------------
# gg + geom_text(aes(label=longID), size=2, data=bib3_sub1) + labs(subtitle="With labels for high-JIF and follow-up empirical papers") + theme(legend.position = "None")   # text
# 
# gg + geom_label(aes(label=longID), size=2, data=bib3_sub1, alpha=0.25) + labs(subtitle="With labels for high-JIF and follow-up empirical papers") + theme(legend.position = "None")  # label

# Plot text and label that REPELS eachother (using ggrepel pkg) ------------
#gg + geom_text_repel(aes(label=longID), size=2, data=bib3_sub1) + labs(subtitle="WWith labels for high-JIF and follow-up empirical papers") + theme(legend.position = "None")   # text

# Add labels
gg <- gg + geom_label_repel(aes(label=longID), size=2, data=bib3_sub1) + labs(subtitle="With labels for high-JIF and follow-up empirical papers") + theme(legend.position = "None")   # label

ggsave("plot_zebrafinch_citing_plot1.pdf")
rm(gg) #clean up
```

```{r plot by year and TC ring labels, eval = TRUE}
# Scale points by JIF (Journal Impact Factor)

# table(is.na(bib2$JIF)) #46 missing - probably for book chapters etc. - remove:
bib3 <- bib2 %>% filter(!is.na(bib2$JIF))

# Filter required rows
bib3_sub2 <- bib3 %>% filter(ring == "yes" | TC > 300, )

# Basic plot
gg <- ggplot(bib3, aes(x=PY, y=TC, size=JIF, alpha=0.1)) + 
  geom_point(aes(col=ring)) +
  theme_minimal() +
  theme(legend.position="top") + 
  guides(colour = FALSE, alpha = FALSE) + guides(size=guide_legend("Journal Impact Factor")) + 
  labs(title="Impact", x="Publication Year", y="Total Citations", caption="Source: Scopus")

# Add labels
gg <- gg + geom_label_repel(aes(label=longID), size=2, data=bib3_sub2) + labs(subtitle="With labels for highly-cited and follow-up empirical papers") + theme(legend.position = "None")   # label

ggsave("plot_zebrafinch_citing_plot2.pdf")
rm(gg) #clean up
```

```{r save data and plots, eval = FALSE}
save(bib2, revdata, file="./data/data_processed.RData")
load("./data/data_processed.RData")
```

#### Initial analyses in bibliometrix

```{r bibliometrix general, eval = FALSE}
# Preliminary descriptive analysis 
results <- biblioAnalysis(bib2, sep = ";")
#summary(object = results, k = 20, pause = FALSE)

# pdf(file = "bib_4descriptive.pdf", height = 8, width = 8, pointsize=10)
# par(mfrow=c(2,2), mar = c(4,4,1,1))
# plot(results, k = 20, pause=FALSE)
# dev.off()

#####################  Figure - CO-AUTHORS NETWORK  ####################################################
#pdf(file="Figure_collaboration_network.pdf", width=8, height=8, pointsize=10)
par(mfrow=c(1,1), mar=c(0,0,0,0))
M <- metaTagExtraction(bib2, Field = "CR_AU", sep = ";")
NetMatrix <- biblioNetwork(M, analysis = "collaboration", network = "authors", sep = ";")
net <- networkPlot(NetMatrix, n = 500, cluster="walktrap", Title = "", labelsize = 0.2, type = "fruchterman", size=TRUE, remove.multiple=TRUE)	
#dev.off() #note, changing n alters the colurs and arrangements of the authors and clusters
###################################################################################

#####################  Figure - HISTORICAL CO-CITATION NETWORK  ####################################################
#pdf(file="Figure_historical_network.pdf", width=8, height=8, pointsize=10)
par(mfrow=c(1,1), mar=c(0,0,0,0))
M <- metaTagExtraction(bib, Field = "CR_AU", sep = ";")
histResults <- histNetwork(M, min.citations = 10, sep = ";") # "n" (number of most cited references to select) picked manually, larger numbers give error
histPlot(histResults, size=TRUE, arrowsize = 0.2) 
#dev.off()
###################################################################################

### CITATIONS

M <- metaTagExtraction(bib2, Field = "CR_AU", sep = ";")

#co-ciation network
NetMatrix <- biblioNetwork(M, analysis = "co-citation", network = "authors", sep = ";")
#NetMatrix <- biblioNetwork(M, analysis = "co-citation", network = "references", sep = ";")
net <- networkPlot(NetMatrix, n = 50, type = "kamada", Title = "Co-Citation", labelsize=0.5) #odd?

## Bipartite network of the existing networkds
# Co-Citation network of the existing studies
CRnet <- cocMatrix(M, Field = "CR", sep = ".  ")
net <- networkPlot(CRnet, n = 50, labelsize = 0.3, size=TRUE, weighted = TRUE)	
##### Error in graph.adjacency.sparse(adjmatrix, mode = mode, weighted = weighted, : not a square matrix

### BIBLIOGRAPHIC COUPLING
NetMatrix <- biblioNetwork (M, analysis = "coupling", network = "references", sep = ";") #invalid dimnames?
net <- networkPlot(NetMatrix, n = 100, cluster="walktrap", Title = "Bibliographic Coupling Network", label = FALSE, labelsize = 1, type = "kamada", size=TRUE, remove.multiple=TRUE)	
# odd - too few connections 

###################################################################################

## THEMATIC MAP
M <- metaTagExtraction(bib2, Field = "CR_AU", sep = ";")
NetMatrix <- biblioNetwork(M, analysis = "co-occurrences", network = "keywords", sep = ";")
S <- normalizeSimilarity(NetMatrix, type = "association")
net <- networkPlot(S, n = 50, Title = "keyword co-occurrence network", type="fruchterman", labelsize = 0.8, halo = TRUE, cluster = "walktrap",remove.isolates=FALSE, remove.multiple=FALSE, noloops=TRUE, weighted=TRUE)

#Conceptual structure
#CS <- conceptualStructure(bib, field="AB", minDegree=5, k.max=5, stemming=FALSE, labelsize=10)	#too dense
```

#### Included papers by Nancy Burley

```{r Burley, eval = TRUE}
grep("BURLEY", bib2$AU, value=TRUE) #we have 14 papers that Burley co-authored, but one is mislabelled as Burley DN
 #fix Burley DN to NT
by_Burley <- bib2 %>% filter(bib2$AU %in% grep("BURLEY", bib2$AU, value=TRUE)) #14 full records (incl. 2 used as initial starting point)
#cbind(by_Burley$AU, by_Burley$PY, by_Burley$TI, by_Burley$SO)
#toadd: 6, 7, 11, 12 #(ZF with ring manipulations) #(original 13, 14)
by_Burley_add <- by_Burley[c(6, 7, 11, 12),] #4 papers to be used to get additional relevant literature (+2 others known to be imporatant, but not captured here)
#cbind(by_Burley_add$PY, by_Burley_add$TI)
```

We have captured 12 papers by Burley via papers citing initial 2 publications by Burley (1981, 1982).    
However, a few other important papers by Burley are missing. We will add these and also the papers citing them to create a more comprehensive literature data set for bibliometric analyses.   

NEXT: collect records of papers citing these 4 extra papers by Burley, the reference for the original 1981 paper and another 2 key papers by Burley (stored in Burley_3extra.bib):    
 * Burley, N., 1981. Sex Ratio Manipulation and Selection for Attractiveness. Science, 211(4483), pp.721–722
 * Sex‐ratio manipulation in color‐banded populations of zebra finches. N Burley - Evolution, 1986    
 * The differential-allocation hypothesis: an experimental test. N Burley - The American Naturalist, 1988    


### Literature (final data set)    

#### Upload additional Scopus data set   
The records are stored in zebrafinch_Scopus2.bib file - first we use bibliometrix and revtools function to load these into a data frame. We then merge this data frame with the journal citation records, deduplicate with the original data frame to get the trurly new records.  

```{r load more biblio data , eval = TRUE}
### 1 Load bib file with records from Scopus (2019/12/27) into bibliometrix package to add to a  data frame for anlayses:
tmp1 <- readFiles("./data/Burley_3extra.bib")
tmp2 <- readFiles("./data/zebrafinch_Scopus2.bib")
# Convert to bibliometric data frames
bibnew1 <- convert2df(tmp1, dbsource = "scopus", format = "bib")
bibnew1$longID <- rownames(bibnew1) #add column with long paper ID made from rownames
bibnew2 <- convert2df(tmp2, dbsource = "scopus", format = "bib")
bibnew2$longID <- rownames(bibnew2) #add column with long paper ID made from rownames
#dim(bibnew2) #618 - ok
bibnew <- bind_rows(bibnew1, bibnew2) #merge the two new dataframes
#length(unique(bibnew$TI)) #620 - we have 2 duplicated records again?
#which(bibnew$TI == bibnew$TI[duplicated(bibnew$TI)]) #rows 101 and 105 are duplicated
#bibnew[c(213, 216),] #same paper, different formatting, remove one with rownames=="TTH A, 2010, ARCH TIERZ"
bibnew <- bibnew %>% filter(longID != "TTH A, 2010, ARCH TIERZ") #remove one of the duplicates
bibnew$TI <- gsub("FINCHES TAENIOPYGIA GUTTATA) ", "FINCHES (TAENIOPYGIA GUTTATA) ", bibnew$TI) #fixing one title

### 2. Load same bib file into revtools creating differentky formatted dat frame (will be used for manual screening/labeling):
revdatanew1 <- read_bibliography("./data/Burley_3extra.bib")
revdatanew2 <- read_bibliography("./data/zebrafinch_Scopus2.bib")
revdatanew <- bind_rows(revdatanew1, revdatanew2) #merge the two new dataframes
#length(unique(revdatanew$title)) #620 - we have 2 duplicated records again?
#revdatanew$label
#length(unique(revdatanew2$title)) #617
#which(duplicated(revdatanew$title)) #row 217
#which(revdatanew$title == revdatanew$title[duplicated(revdatanew$title)]) #rows 214 and 217
#revdatanew[c(214, 217),] # same paper, different formatting, remove one with label==Tth2010328.1
revdatanew <- revdatanew %>% filter(label != "Tth2010328.1") #remove one of the duplicates
revdatanew$title <- gsub("  ", " ", revdatanew$title) #remove double space from one of the titles
revdatanew$title <- gsub(" \\{taeniopygia guttata) ", " (taeniopygia guttata) ", revdatanew$title) #fixing one title

#compare data frame created in revtools with data frame created in bibliometrix
#length(intersect(tolower(revdatanew$title), tolower(bibnew$TI))) #620 - all matching titles (at lower case)
#setdiff(tolower(revdatanew$title), tolower(bibnew$TI)) #0 mismatches
#setdiff(tolower(bibnew$TI), tolower(revdatanew$title)) #0 mismatches

#write.csv(revdatanew, "./data/Scopus_bibnew_as_df.csv", row.names = FALSE) #sve as Rdat, as csv messes up rows!
```

#### Incorporate journals IF   
Adding data with journal impact factors (InCite Journal Citation Reports:  Selected JCR Year: 2018 Selected Editions: SCIE,SSCI Selected Category Scheme: WoS).   

```{r journals again, eval = TRUE}
#load journal data
journals_data <- read_excel("./data/JournalHomeGrid.xlsx", na = "NA", skip = 2, col_types = c("numeric", "text", "numeric", "skip", "numeric", "numeric")) %>% mutate_if(is.character, as.factor)
#names(journals_data)
#remove unnecessary columns and rename the other
#journals_data <- journals_data  %>% select(-"...4")
journals_data <- journals_data  %>% rename(Journal_Name = "Full Journal Title", 
                       Total_Cites = "Total Cites",
                       JIF = "Journal Impact Factor",
                       Eigenfactor_Score = "Eigenfactor Score"
                       )
journals_data <- mutate(journals_data, Journal_Name_lower = tolower(Journal_Name))
#check journal names
journals <- bibnew$SO #402
journals_list <- unique(tolower(journals)) #130
intersect(journals_list, journals_data$Journal_Name_lower) #85
#setdiff(journals_list, journals_data$Journal_Name_lower) #50 unmatched, many books
#fix journal names (Scopus = JCR):
journals_data$Journal_Name_lower[grepl("ethology", journals_data$Journal_Name_lower)]
journals_data$Journal_Name_lower <- gsub("proceedings of the royal society b-biological sciences", "proceedings of the royal society b: biological sciences", journals_data$Journal_Name_lower, ignore.case = TRUE)
journals_data$Journal_Name_lower <- gsub("philosophical transactions of the royal society b-biological sciences", "philosophical transactions of the royal society b: biological sciences", journals_data$Journal_Name_lower, ignore.case = TRUE)
journals_data$Journal_Name_lower <- gsub("trends in ecology & evolution", "trends in ecology & evolution"
, journals_data$Journal_Name_lower, ignore.case = TRUE)
journals_data$Journal_Name_lower <- gsub("annual review of ecology evolution and systematics", "annual review of ecology and systematics", journals_data$Journal_Name_lower, ignore.case = TRUE)
journals_data$Journal_Name_lower <- gsub("ethology ecology & evolution", "ethology ecology and evolution", journals_data$Journal_Name_lower, ignore.case = TRUE)
journals_data$Journal_Name_lower <- gsub("emu-austral ornithology", "emu", journals_data$Journal_Name_lower, ignore.case = TRUE)

#marge journal info into bibnew dataframe
bibnew <- mutate(bibnew, Journal_Name_lower = tolower(SO))
bibnew <- left_join(bibnew, journals_data, by = "Journal_Name_lower")
#dim(bibnew) #631 - note some records were joined incorrectly (some duplicated data rows)!
#table(duplicated(bibnew$TI))
#bibnew <- distinct(bibnew, .keep_all = TRUE) #does not work
length(unique(bibnew$TI)) #619
#bibnew$TI[which(bibnew$TI %in% bibnew$TI[duplicated(bibnew$TI)])] #duplicated titles
#View(bibnew[which(bibnew$TI %in% bibnew$TI[duplicated(bibnew$TI)]), ] ) #duplicated full records
bibnew2 <- bibnew %>% filter(!duplicated(bibnew$TI))
#dim(bibnew2) #619 ok
write.csv(bibnew2, "./data/Scopus_bibnew_as_df.csv", row.names = FALSE)
rm(journals_data) #clean up
```

#### Data clean-up: check author names for additional records  

Note: Burley appears again both as "BURLEY N" and "BURLEY NT"! (similar issue for some other outhors)   
```{r authors again, eval = TRUE}
#check author names as strings
authors <- bibnew2$AU #402 
#extract individual authors of citing papers into a vector of names
authors2 <- unlist(strsplit(authors, ";")) #these are authors in the reference lists!
authors2 <- unique(authors2[order(authors2)]) #see which names need cleaning
#write.csv(authors2, "./data/author_list_uncleaned_new.csv", row.names = FALSE)

#grep("BURLEY", authors2, value=TRUE) #3 forms - needs fixing

# We can do some cleaning where we suspect a mistake (especially author initials)
corrected <- paste(bibnew2$AU, ";", sep="")
corrected <- gsub("BURLEY N;", "BURLEY NT;", corrected, ignore.case = TRUE)
corrected <- gsub("BURLEY DN;", "BURLEY NT;", corrected, ignore.case = TRUE)
corrected <- gsub("CASPERS B;", "CASPERS BA;", corrected, ignore.case = TRUE)
corrected <- gsub("ALONSO LVAREZ C;", "ALONSO ALVAREZ C;", corrected, ignore.case = TRUE)
corrected <- gsub("CUTHILL I;", "CUTHILL IC;", corrected, ignore.case = TRUE)
corrected <- gsub("JENNIONS M", "JENNIONS MD", corrected, ignore.case = TRUE)
corrected <- gsub("TINBERGEN J;", "TINBERGEN JM;", corrected, ignore.case = TRUE)
corrected <- gsub("ZANN R;", "ZANN RA;", corrected, ignore.case = TRUE)
bibnew2$AU <- corrected #add corrections

#write.csv(bibnew2, "Scopus_bibnew_as_df.csv", row.names = FALSE) #sve as Rdat, as csv messes up rows!
```

**Extended Data Table 2:**   
List of 619 additional bibliographic records used in the analyses (from 6 more key papers by Burley published 1986-1996).    

```{r scrollable table of 402 papers, include = FALSE, eval = FALSE}
bibnew %>% select(AU, PY, TI, SO, VL, PP, DT) %>% kable("html") %>%
    kable_styling("striped", position = "left") %>%
  scroll_box(width = "100%", height = "300px")
```

#### Matching dataframes to locate new records (unscreened) records for labelling in revtools   

```{r matching revdata, include = TRUE, eval = TRUE}
#by title:
#length(intersect(tolower(revdata$title), tolower(revdatanew$title))) #141 overlapping
#length(setdiff(tolower(revdata$title), tolower(revdatanew$title))) #260 unique in revdata
#length(setdiff(tolower(revdatanew$title), tolower(revdata$title))) #478 unique in revdatanew
#create subset of new records to screen
toscreen <- revdatanew %>% filter(tolower(revdatanew$title) %in% setdiff(tolower(revdatanew$title), tolower(revdata$title)))
#dim(toscreen) #478
#write.csv(toscreen, "./data/SCR_ABS_LAB_RES_toscreen_set2.csv", row.names = FALSE)
```

#### Coding contents of papers using Revtools - for the new records    
Revtools has a screening tool which can be also used for adding lebels to records.   
Manually screened records to mark these on birds and coloured ring preference/reproductionas (labelled as "included", with additional marks for zebrafinch "zf" and other birds "ob").     

```{r screen and label in revtools again, eval = FALSE}
scr_tit_res_set2 <- screen_titles(toscreen) # run revtools app with titles only - exported to zebrafinch_title_screening_res_set2.csv
names(scr_tit_res_set2)
table(scr_tit_res_set2$screened_titles) #67 not excluded
scr_abs_set2 <- scr_tit_res_set2 %>% filter(screened_titles != "excluded") #filter out 62 abstracts that are not excluded for further screening
scr_abs_res_set2 <- screen_abstracts(scr_abs_set2) # run revtools app with abstracts
names(scr_abs_res_set2)
table(scr_abs_res_set2$screened_abstracts) #4 selected
scr_abs_lab_set2 <- scr_abs_res_set2 %>% filter(screened_abstracts != "excluded") #filter out 32 abstracts that are not excluded for manual labeling
#View(scr_abs_lab_set2) #they are all on zebrafinch
#dim(scr_abs_lab_set2)
scr_abs_lab_set2$notes <- "ZF"
write.csv(scr_abs_lab_set2, "./data/SCR_ABS_LAB_RES_set2.csv", row.names = FALSE)
```

```{r add screening labels from revtools, eval = TRUE}
scr_abs_lab_res_set2 <- read.csv("./data/SCR_ABS_LAB_RES_set2.csv")
#names(scr_abs_lab_res_set2)
#table(scr_abs_lab_res_set2$notes) #ZF 4
bibnew3 <- bibnew2 %>% mutate(ring = ifelse(tolower(bibnew2$TI) %in% tolower(scr_abs_lab_res_set2$title), "yes", "no"))
#table(bibnew3$ring) # 4 yes, 615 no
```

```{r merge bib2 and binew3, eval = TRUE}
bib4 <- bind_rows(bib2, bibnew3)
#dim(bib4) #1021 41
#table(bib4$ring) #36 "yes", but some ar not ring studies
```

With original and follow-up birds ring preference studies in blue and labels:

```{r prepare for plotting, eval = FALSE}
# table(is.na(bib4$JIF)) #107 missing JIF- probably for book chapters etc., including Burley 1981 (discontinued journal: "The Sciences was published from 1961 to 2001")
#bib5 <- bib4 %>% mutate(JIF = replace(JIF, which(is.na(JIF)), 0)) #assign JIF=0 to all missing values, including Burley 1981

bib5 <- bib4 %>% filter(!is.na(bib4$JIF)) #careful, this used to remove Burley 1981 before journal name was fixed

grep("BURLEY", bib5$AU, value=TRUE) #we have 69 publications that Burley co-authored
Burley <- bib5 %>% filter((bib5$AU %in% grep("BURLEY", bib5$AU, value=TRUE)))
Burley_ring <- bib5 %>% filter((bib5$AU %in% grep("BURLEY", bib5$AU, value=TRUE)) & ring=="yes") 
#Burley_ring #8 records of "ring" studies by Burley

Nature_Science <- bib5 %>% filter(SO %in% c("NATURE", "SCIENCE"))
#dim(Nature_Science) #16 papers
Nature_Science_ring <- bib5 %>% filter(SO %in% c("NATURE", "SCIENCE") & ring=="yes")
#dim(Nature_Science_ring) #3 papers

highJIF <- bib5 %>% filter(JIF > 40)
#dim(highJIF) #16 papers
highJIF_ring <- bib5 %>% filter(JIF > 40 & ring=="yes")
#dim(highJIF_ring) #3 papers

highlycited <- bib5 %>% filter(TC > 200)
#dim(highlycited) #30 papers
highlycited_ring <- bib5 %>% filter(TC > 200 & ring=="yes")
#dim(highlycited_ring) #3 papers
```

```{r plot by year and IF ring labels new, eval = FALSE}
# scaling points by TC (total citations), blue color - empirical "colour ring" stdudies
gg <- ggplot(bib5, aes(x = PY, y = JIF, size = TC, alpha = 0.1)) + 
  geom_point(aes(col=ring)) + 
  theme_minimal() +
  theme(legend.position="bottom") + 
  labs(title="A.", x="Publication Year", y="Journal Impact Factor", caption="Source: Scopus, Dec 2019")
# add point labels
gg <- gg + geom_label_repel(aes(label=longID), size=2, data=Burley_ring) + labs(subtitle="") + theme(legend.position = "bottom") 
gg <- gg + geom_label_repel(aes(label=longID), size=2, data=highJIF) + labs(subtitle="") + theme(legend.position = "bottom")
gg <- gg + guides(alpha = FALSE) + guides(size=guide_legend("Journal IF:"), colour = guide_legend("''ring'' papers:")) 
gg

ggsave("./plots/plot_zebrafinch_citing_plot_A.pdf", width = 14, height = 6, units = "in", dpi = 1800)
rm(gg) #clean up
```

```{r plot by year and TC ring labels, eval = TRUE}
# scaling points by JIF (Journal Impact Factor)
gg <- ggplot(bib5, aes(x=PY, y=TC, size=JIF, alpha=0.1)) + 
  geom_point(aes(col=ring)) +
  theme_minimal() +
  theme(legend.position="bottom") + 
  labs(title="B.", x="Publication Year", y="Total Citations", caption="Source: Scopus, Dec 2019")

# add point labels
gg <- gg + geom_label_repel(aes(label=longID), size=2, data=Burley_ring) + labs(subtitle="") + theme(legend.position = "bottom") 
gg <- gg + geom_label_repel(aes(label=longID), size=2, data=highlycited_ring) + labs(subtitle="") + theme(legend.position = "bottom")
gg <- gg + guides(alpha = FALSE) + guides(size=guide_legend("Journal IF:"), colour = guide_legend("''ring'' papers:")) 
gg

ggsave("./plots/plot_zebrafinch_citing_plot_B.pdf", width = 14, height = 6, units = "in", dpi = 1800)
rm(gg) #clean up
```

```{r save data and plots, eval = FALSE}
save(bib4, bib5, revdatanew, file="./data/data_processed_new.RData")
#load("./data/data_processed_new.RData")
```

#### Analyses in bibliometrix

```{r bibliometrix general, eval = FALSE}
# Preliminary descriptive analysis on 1022 documents - TODO: SUMMARY TABLE????
results <- biblioAnalysis(bib5, sep = ";")
#summary(object = results, k = 20, pause = FALSE)

# pdf(file = "bib_4descriptive.pdf", height = 8, width = 8, pointsize=10)
# par(mfrow=c(2,2), mar = c(4,4,1,1))
# plot(results, k = 20, pause=FALSE)
# dev.off()

#####################  Figure - CO-AUTHORS NETWORK  ####################################################
par(mfrow=c(1,1), mar=c(0,0,0,0))
M <- metaTagExtraction(bib5, Field = "CR_AU", sep = ";")
NetMatrix <- biblioNetwork(M, analysis = "collaboration", network = "authors", sep = ";")
#pdf(file="./plots/Figure_collaboration_network.pdf", width=10, height=8, pointsize=10, family="Bookman")
net <- networkPlot(NetMatrix, n = 100, cluster="walktrap", Title = "", labelsize = 0.8, type = "fruchterman", size=TRUE, remove.multiple=TRUE, edgesize = 2)	
#dev.off() #note, changing n alters the colurs and arrangements of the authors and clusters
###################################################################################

#####################  Figure - HISTORICAL CO-CITATION NETWORK  ####################################################
par(mfrow=c(1,1), mar=c(0,0,0,0))
M <- metaTagExtraction(bib, Field = "CR_AU", sep = ";")
histResults <- histNetwork(M, min.citations = 5, sep = ";") # "n" (number of most cited references to select) picked manually, larger numbers give error
#pdf(file="./plots/Figure_historical_co-citation_network.pdf", width=8, height=8, pointsize=10)
histPlot(histResults, size=TRUE, arrowsize = 0.2) 
#dev.off() #nte the automatic plot caption does not make sense
###################################################################################

### CITATIONS

M <- metaTagExtraction(bib5, Field = "CR_AU", sep = ";")

#co-ciation network
NetMatrix <- biblioNetwork(M, analysis = "co-citation", network = "authors", sep = ";")
#NetMatrix <- biblioNetwork(M, analysis = "co-citation", network = "references", sep = ";")
net <- networkPlot(NetMatrix, n = 50, type = "kamada", Title = "Co-Citation", labelsize=0.5) #odd?

## Bipartite network of the existing networkds
# Co-Citation network of the existing studies
CRnet <- cocMatrix(M, Field = "CR", sep = ".  ")
net <- networkPlot(CRnet, n = 50, labelsize = 0.3, size=TRUE, weighted = TRUE)	
##### Error in graph.adjacency.sparse(adjmatrix, mode = mode, weighted = weighted, : not a square matrix

### BIBLIOGRAPHIC COUPLING
NetMatrix <- biblioNetwork (M, analysis = "coupling", network = "references", sep = ";") #invalid dimnames?
net <- networkPlot(NetMatrix, n = 100, cluster="walktrap", Title = "Bibliographic Coupling Network", label = FALSE, labelsize = 1, type = "kamada", size=TRUE, remove.multiple=TRUE)	
# odd - too few connections 

###################################################################################

## THEMATIC MAP
M <- metaTagExtraction(bib5, Field = "CR_AU", sep = ";")
NetMatrix <- biblioNetwork(M, analysis = "co-occurrences", network = "keywords", sep = ";")
S <- normalizeSimilarity(NetMatrix, type = "association")
net <- networkPlot(S, n = 50, Title = "keyword co-occurrence network", type="fruchterman", labelsize = 0.8, halo = TRUE, cluster = "walktrap",remove.isolates=FALSE, remove.multiple=FALSE, noloops=TRUE, weighted=TRUE)

#Conceptual structure
CS <- conceptualStructure(bib5, field="AB", minDegree=5, k.max=5, stemming=FALSE, labelsize=10)	#too dense
```
